% REPLACE WITH YOUR MASTER RESUME


%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Template for general use
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Your Name} \\ \vspace{1pt}
    \small \href{mailto:your.email@example.com}{\underline{your.email@example.com}} $|$
    \href{https://github.com/yourusername}{\underline{github.com/yourusername}} $|$
    \href{https://linkedin.com/in/yourprofile}{\underline{linkedin.com/in/yourprofile}} \\ \vspace{3pt}
    \small Software Engineer · Full Stack Developer · Cloud Infrastructure
\end{center}
\vspace{-15pt}

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, JavaScript, TypeScript, Java, C++, Go, SQL \\
     \textbf{Technologies:} React, Node.js, Docker, Kubernetes, AWS, PostgreSQL, MongoDB \\
     \textbf{Tools:} Git, Linux, CI/CD, Terraform, REST APIs
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Company Name}{Month YYYY -- Month YYYY}
      {Software Engineering Intern}{City, State}
      \resumeItemListStart
        \resumeItem{Developed and maintained web applications using \textbf{React} and \textbf{Node.js}, improving user experience and application performance.}
        \resumeItem{Implemented RESTful APIs and integrated with \textbf{PostgreSQL} database, ensuring efficient data retrieval and storage.}
        \resumeItem{Collaborated with cross-functional teams to deliver features on time and participated in code reviews to maintain code quality.}
        \resumeItem{Utilized \textbf{Docker} for containerization and deployed applications on cloud platforms, reducing deployment time by 30\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Another Company}{Month YYYY -- Month YYYY}
      {Full Stack Developer}{City, State}
      \resumeItemListStart
        \resumeItem{Built scalable microservices architecture using \textbf{Kubernetes} and \textbf{Docker}, improving system reliability and scalability.}
        \resumeItem{Designed and implemented database schemas using \textbf{PostgreSQL} and optimized queries, reducing response time by 40\%.}
        \resumeItem{Developed responsive frontend components using \textbf{React} and \textbf{TypeScript}, enhancing user interface and accessibility.}
        \resumeItem{Implemented CI/CD pipelines using \textbf{GitHub Actions}, automating testing and deployment processes.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Project Name} $|$ \emph{React, Node.js, PostgreSQL}}{Month YYYY}
      \resumeItemListStart
        \resumeItem{Built a full-stack web application using \textbf{React} for the frontend and \textbf{Node.js} with \textbf{Express} for the backend.}
        \resumeItem{Implemented user authentication and authorization using JWT tokens, ensuring secure access to protected routes.}
        \resumeItem{Designed and implemented a \textbf{PostgreSQL} database schema, optimizing queries for improved performance.}
        \resumeItem{Deployed the application using \textbf{Docker} containers on cloud infrastructure, achieving 99.9\% uptime.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Another Project} $|$ \emph{Python, FastAPI, MongoDB}}{Month YYYY}
      \resumeItemListStart
        \resumeItem{Developed a RESTful API using \textbf{FastAPI} with async/await patterns, handling 1000+ requests per second.}
        \resumeItem{Integrated with \textbf{MongoDB} for flexible document storage and implemented caching using Redis.}
        \resumeItem{Containerized the application with \textbf{Docker} and set up CI/CD pipelines for automated testing and deployment.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Third Project} $|$ \emph{TypeScript, React, AWS}}{Month YYYY}
      \resumeItemListStart
        \resumeItem{Created a responsive web application using \textbf{React} and \textbf{TypeScript}, ensuring type safety and improved developer experience.}
        \resumeItem{Deployed static assets to \textbf{AWS S3} with CloudFront CDN, reducing load times by 50\%.}
        \resumeItem{Implemented automated testing using Jest and React Testing Library, achieving 85\% code coverage.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
% Uncomment and fill in if you have publications
% \section{Publications}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {Paper Title}{Month YYYY}
%       {Research Paper}{}
%       \resumeItemListStart
%         \resumeItem{Description of your research contribution and findings.}
%       \resumeItemListEnd
%   \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University Name}{YYYY -- YYYY}
      {Bachelor of Science in Computer Science · GPA: X.X/4.0}{}
      \resumeItemListStart
        \resumeItem{Relevant coursework: Algorithms, Data Structures, Object-Oriented Programming, Databases, Software Engineering, Operating Systems, Computer Networks}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

«
